### 2021-06-07 README.rmd
correcting a typo in README

* *Silhouette.index*: the silhouette index (`fclust::SIL.F`)
* *Partition.entropy*: the partition entropy index (`fclust::PE`)
* *Partition.coeff*: the partition entropy coefficient (`fclust::PC`)
* *Modified.partition.coeff*: the modified partition entropy coefficient (`fclust::MPC`)
* *XieBeni.index*: the Xie and Beni index (`fclust::XB`)
* *FukuyamaSugeno.index*: the Fukuyama and Sugeno index (`geocmeans::calcFukuyamaSugeno`)
* *DavidBoulin.index*: the David-Boulin index (`geocmeans::calcDavidBouldin`)
* *CalinskiHarabasz.index*: the Calinski-Harabasz index (`geocmeans::calcCalinskiHarabasz`)
* *GD43.index* and *GD53.index*: two version of the generalized Dunn index (`geocmeans::calcGD43` and `calcGD45`)
* *Negentropy.index*: the Negentropy Increment index (`geocmeans::calcNegentropyI`)
* *Explained.inertia*: the percentage of total inertia explained by the solution

>>>>

* *Silhouette.index*: the silhouette index (`fclust::SIL.F`)
* *Partition.entropy*: the partition entropy index (`fclust::PE`)
* *Partition.coeff*: the partition entropy coefficient (`fclust::PC`)
* *Modified.partition.coeff*: the modified partition entropy coefficient (`fclust::MPC`)
* *XieBeni.index*: the Xie and Beni index (`fclust::XB`)
* *FukuyamaSugeno.index*: the Fukuyama and Sugeno index (`geocmeans::calcFukuyamaSugeno`)
* *DavidBoulin.index*: the David-Boulin index (`geocmeans::calcDavidBouldin`)
* *CalinskiHarabasz.index*: the Calinski-Harabasz index (`geocmeans::calcCalinskiHarabasz`)
* *GD43.index* and *GD53.index*: two version of the generalized Dunn index (`geocmeans::calcGD43` and `calcGD53`)
* *Negentropy.index*: the Negentropy Increment index (`geocmeans::calcNegentropyI`)
* *Explained.inertia*: the percentage of total inertia explained by the solution
